%______________________________________________________________________________________________________________________
\documentclass[margin, line]{resume}
%______________________________________________________________________________________________________________________
\begin{document}
 {\Large Yi Qian}
    \hfill 3270 A.V. Williams       \quad \quad  \quad \quad \quad \quad  \quad \quad \quad \quad  \quad \quad  \,\,\,    \vspace{0mm}\\\vspace{0mm}%
    \hfill University of Maryland        \quad \quad \,\,     mobile: (518)522-7333         \vspace{0mm}\\\vspace{0mm}%
    \hfill College Park, MD 20740         \quad       email: yiqian@cs.umd.edu   \vspace{0mm}\\\vspace{0mm}%
  %  \hfill USA         \quad \quad  \quad \quad      www.rpi.edu/$\sim$qiany3  \vspace{0mm}\\\vspace{-4mm}%
    
\begin{resume}
  
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
    Security, Applied Cryptology, Algorithms and Social Networking\
    

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    {\sl Ph.D.}, Computer Science \quad \quad \quad  \quad  \quad Advisor: Elaine Shi \hfill Expected May 2017\\
     \vspace{-2mm}University of Maryland, College Park, MD  \hfill  GPA: 3.93/4.0\\ \\
    {\sl M.S.}, Computer Science \quad \quad \quad  \quad  \quad Advisor: Sibel Adali \hfill May 2013\\
     \vspace{-2mm}Rensselaer Polytechnic Institute (RPI), Troy, NY  \hfill  GPA: 3.88/4.0\\ \\
     {\sl B.E. with Honors}, Electrical Engineering \hfill June 2010\\ 
    Elite Class of Electrical Engineering (Chien-Shiung Wu College)\\
    Southeast University, Nanjing, China \hfill GPA: 3.7/4.0

   %__________________________________________________________________________________________________________________
    % Research Experience
    \section{\mysidestyle Research}
    \textbf{Research Assistant} \quad Department of Computer Science, UMD \hfill {Mar. 2014 -- Present}\\
     \textsl{Differentially Private Streaming Mechanism} \\
     \vspace{-2mm}$\bullet$ Conduct mechanism designs that are differentially private in the streaming setting.
     
     \textsl{Abstraction of Streaming Authenticated Data Structures}\\
     $\bullet$ Constructed an abstraction of the Data Structures to render it applicable to various instantiations. \\
      \vspace{-2mm}$\bullet$ Developed and implemented a practical instantiation of the scheme. 
     
           
    \textbf{Research Assistant} \quad Department of Computer Science, RPI \hfill {Sept. 2010 -- May 2013}\\
     \textsl{General Triadic Balance and Convergence Model in Social Networks}\\
      $\bullet$ Proposed an extended balance theory on General Triadic Balance and Convergence Model in Social Networks.\\
      $\bullet$ Applied the proposed extended balance theory to mathematically justify some well-observed social network phenomena.\\
      \vspace{-2mm}$\bullet$ Experimentally tested the theory in predicting edge signs on real social network datasets.
      
       \textsl{Provenance based Trust Reasoning}\\
      \vspace{-2mm}$\bullet$ Designed a provenance based trust reasoning mechanism.
                
   %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Publications}
    Streaming Authenticated Data Structures: Abstraction and Implementation.
    \textsl{CCSW}, Pages 129-139, 2014.
    
    Foundations of Trust and Distrust in Networks: Extended Structural Balance Theory.
    \textsl{ACM Transactions on the Web (TWEB)}, Volume 8 Issue 3, June 2014.
    
    Extended Structural Balance Theory for Modeling Trust in Social Networks.
    \textsl{Eleventh International Conference on Privacy, Security and Trust}, Spain. 2013.
    
  \vspace{-2mm}
    Extended Balance Theory and Convergence Model in Social Networks.
    \textsl{Master Thesis}, RPI, Troy NY. 2013.

\vspace{-2mm}
    A Unified Framework for Trust in Composite Networks.
    \textsl{Proceedings of 14th International Workshop on Trust in Agent}, Tapei, Taiwan. 2011. 
    
    %__________________________________________________________________________________________________________________
    % Teaching Experience
    \section{\mysidestyle Teaching}
     \textbf{Teaching Assistant} \quad Department of Computer Science, UMD \hfill {Sept. 2013 -- Sept. 2014}\\
     \textsl{Discrete Structure, Organization of Programming Languages}\\
     \vspace{-2mm}$\bullet$ Gave lectures and led discussions on problems weekly.
      
      
      \textbf{Teaching Assistant} \quad Department of Computer Science, RPI \hfill {Spring 2012, Spring 2013}\\
     \vspace{-2mm}\textsl{Computer Algorithm}, \textsl{Foundation of Computer Science} 
    
    %__________________________________________________________________________________________________________________
    % Relevant Courses
    %\section{\mysidestyle Relevant \\Courses} 

    %Computer Algorithm  \\  
    %$\bullet$ Greedy, Dynamic Programming, Network Flow, NP-hardness.\\%
    %Computability and Complexity  \\%
    %$\bullet$ Turing Machine, Solvability, Reducibility, NP-completeness.\\
    %Approximation Algorithms \\  
    %$\bullet$ LP Rounding, Primal-Dual,  Metric Embedding, SDP Rounding, Hardness of Approximation.\\%                       
    %Randomized Algorithm\\ 
    %$\bullet$ Chernoff Bounds, Probabilistic Method, Lovasz Local Lemma, Markov Chains, Freivald’s Technique\\%
    %Graph Theory\\
    %$\bullet$ Matchings, Connectivity, Graph Colorings, Hamiltonian Cycles, Planarity

    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards} 
    Dean Fellowship, University of Maryland College Park  \hfill Sept. 2013-Sept. 2014           \\%
    Outstanding Undergraduate Thesis Award, Southeast University   \hfill July 2010           \\%
    University-level Scholarships, Southeast University   \hfill Sept. 2006-July 2010 
    
   %__________________________________________________________________________________________________________________
    % Presentations 
    \section{\mysidestyle Presentations} 
     ACM Workshop on Cloud Computing Security, Scottsdale, Arizona \hfill Nov. 2014
     %{\sl6th Sino-Singapore Undergraduate Exchange}, Singapore City \hfill Mar. 2009\\
     %{\sl IOSTE Regional Symposium on Science Education}, University of Philippines, Philippines\hfill July 2007
     
    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Skills} 
    Java, Python, C, C++, Ruby, OCaml, Prolog, Matlab, Linux shell scripting, \LaTeXe. 

\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

